### 2019-05-15 2-Chapters/2-Chapter/chapter2.tex
Je ne sais juste pas quoi écrire c'est horrible

We first illustrate in Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem} the current state of the game at time $t=24$.
% Currently at time $t=24$ (out of $T=100$ total time steps),
At this step, the player has collected a sum of rewards of $14$, by observing $X(t) = [6,2,2,2,2]$ rewards of value $1$ in the $K=5$ different arms. Arms were sampled $N(t) = [8,4,4,4,4]$ times, meaning that the value $0$ was seen respectively $[2,2,2,2,2]$ times, and currently arm $1$ appears to be the best one. The true means of the arms are $\bm{\mu}=[0.6, 0.2, 0.55, 0.7, 0.5]$, and (much) more samples are needed before the player can accurately identify arm $4$ as the best arm.
%
We also illustrate in Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem__step100} the result of an example of run, when the player was following the \UCB{} algorithm from \cite{Auer02}.
After $T=100$ steps, the player obtained a cumulated reward of $56$, by playing mostly arms $4,3,5,1,0$ (in decreasing order of number of plays). The empirical means $\widehat{\mu_k}(T)$ correctly identify the best arm (arm $4$), but do not correctly rank the arms as arms $1$ and $3$ obtained means of $\widehat{\mu_1}(T) = 0.5 < \widehat{\mu_3}(T)=0.6$ but the true means are $\mu_3 = 0.55 < \mu_1 = 0.6$

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.75\linewidth]{2-Chapters/2-Chapter/Images/example_of_a_5_arm_bandit_problem.png}
    \caption{Screenshot of the demonstration available online on my website, for a current step of $t=24$. See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}.}
    \label{fig:2:example_of_a_5_arm_bandit_problem}
\end{figure}

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.75\linewidth]{2-Chapters/2-Chapter/Images/example_of_a_5_arm_bandit_problem__step100.png}
    \caption{Screenshot of the demonstration, after the end of the game, after $t=T=100$ steps.}
    \label{fig:2:example_of_a_5_arm_bandit_problem__step100}
\end{figure}

>>>>

We first illustrate in Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem} the current state of the game at time $t=24$.
% Currently at time $t=24$ (out of $T=100$ total time steps),
At this step, the player has collected a sum of rewards of $14$, by observing $X(t) = [6,2,2,2,2]$ rewards of value $1$ in the $K=5$ different arms. Arms were sampled $N(t) = [8,4,4,4,4]$ times, meaning that the value $0$ was seen respectively $[2,2,2,2,2]$ times, and currently arm $1$ appears to be the best one. The true means of the arms are $\bm{\mu}=[0.6, 0.2, 0.55, 0.7, 0.5]$, and (much) more samples are needed before the player can accurately identify arm $4$ as the best arm.
%
We also illustrate in Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem__step100} the result of an example of run, when the player was following the \UCB{} algorithm from \cite{Auer02}.
After $T=100$ steps, the player obtained a cumulated reward of $56$, by playing mostly arms $4,3,5,1,0$ (in decreasing order of number of plays). The empirical means $\widehat{\mu_k}(T)$ correctly identify the best arm (arm $4$), but do not correctly rank the arms as arms $1$ and $3$ obtained means of $\widehat{\mu_1}(T) = 0.5 < \widehat{\mu_3}(T)=0.6$ but the true means are $\mu_3 = 0.55 < \mu_1 = 0.6$.

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.95\linewidth]{2-Chapters/2-Chapter/Images/example_of_a_5_arm_bandit_problem.png}
    \caption{Screenshot of the demonstration available online on my website, for a current step of $t=24$. See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}.}
    \label{fig:2:example_of_a_5_arm_bandit_problem}
\end{figure}

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.95\linewidth]{2-Chapters/2-Chapter/Images/example_of_a_5_arm_bandit_problem__step100.png}
    \caption{Screenshot of the demonstration, after the end of the game, after $t=T=100$ steps.}
    \label{fig:2:example_of_a_5_arm_bandit_problem__step100}
\end{figure}
